---
title: "Project Performance"
subtitle: "Predict gestational diabetes"
author: "Jiang Li"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    df_print: paged
    keep_md: yes
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning  = FALSE)
knitr::opts_knit$set(root.dir = "GDM/" )
```

## Load Data

We will use [ProjectTemplate](http://projecttemplate.net/) to layout my project. When load the project, we will split the **diabetes** dataset into train and test dataset, namely **trainDat** (70%) and **testDat**(remaining 30%).

```{r load,cache=FALSE}
library(ProjectTemplate)
load.project()
ls()
```

## Explore data

In this analysis, we will look at each feature to test whether the average (median) value is different between diabetes patients and normal people. We would apply both t-test(**t.test**) and Wilcoxon Rank Sum (**wilcox.test**).

```{r explore,fig.keep='all'}
head(diabetes)
source("src/explore.R")
```




## Naive Bayes

We only get **78%** and **73%** accuracy on the tain and test dataset.

```{r nv,cache=TRUE}
source("src/funs.R")
get.performance(trainDat,trainDat,algo = "nb")
get.performance(trainDat,testDat,algo = "nb")

```





